A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-13 paper/paper.tex
Added Ciaran's draft introduction (fixing citations)

Given graphs $G$ and $H$, the \emph{Maximum Common Subgraph (MCS)} problem is
to find a graph with as many vertices as possible that is isomorphic to induced
subgraphs of both $G$ and $H$.

MCS has numerous applications, including finding the similarity between organic
molecules, \dots

This paper introduces a new branch and bound algorithm for MCS that improves
state-of-the-art run times on unlabelled, undirected instances by well over an
order of magnitude, and uses only quadratic memory in the order of the input
graphs, allowing us to solve larger instances than previously possible.

>>>>

To determine the similarity or difference between two graphs, we must first
find what they have in common
\citep{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,KriegeThesis}.
The \emph{maximum common subgraph} family of problems involves finding a large
graph which is isomorphic to subgraphs of two given graphs simultaneously.
Because graphs are widely used to model real-world phenomena, maximum common
subgraph problems have arisen in ...  The problems are NP-hard, and remain
challenging computationally. Recent practical progress has been made by using
constraint programming
\citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}, by reducing to the
maximum clique problem \citep{LeviG,DBLP:conf/cp/McCreeshNPS16}, and
by adapting subgraph isomorphism algorithms \citep{UpcomingAAAIPaper}. This paper
introduces a new branch and bound algorithm which exploits special properties
of these problems to allow a much faster exploration of the search space,
whilst retaining the filtering and bounding benefits of the constraint
programming approach. We describe the algorithm for the basic maximum common
subgraph problem, and discuss how it may be adapted to handle vertex labels,
edge labels, and the requirement that the found subgraph be connected. We then
present an empirical study of the algorithm, demonstrating that it improves the
state of the art by more than an order of magnitude on the unlabelled variant
of the problem, and showing that it can handle much larger instances than
earlier constraint programming or clique approaches due to lower memory usage.
